Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-12-16 R0V0.tex
Item 6

\mypara In terms of dynamic programming, the problem of design controllers having an arbitrary structure is known to be NP-hard \cite{BlondelTsitsiklis1997,Tanaka2011}, for linear systems. Consequently, for nonlinear systems the problem is very challenging.

>>>>

\mypara In terms of semidefinite programming, the problem of design controllers having an arbitrary structure is known to be NP-hard \cite{BlondelTsitsiklis1997,Tanaka2011}, for linear systems. Consequently, for nonlinear systems the problem is very challenging.
